\input{preamble}

\begin{document}
\maketitle

\thispagestyle{empty}
\section*{Introduction}

\lettrine[findent=2pt]{\textbf{O}}{ }h Boy! Topology! The one class that absolutely kicked my ass. If you happened to come across this ``glossary" and only know the word ``Topology" from the ``coffee cup is a doughnuts" joke. Well, I have bad news and good news for ya:
\begin{enumerate}
    \item[B).] You won't see and ``coffee cups" or ``doughnuts" for quite some time;
    \item[G).] But you are going to enjoy all the materials nonetheless, and you'll love ``doughnut" as an object for the rest of your life, spoiler alert: it's called a $2$-D Torus. 
\end{enumerate}

Truth is, you need to have some Analysis background with proofs experience, and remember, you best friend and worst enemy $\dfrac{1}{n}$.

My thought of topologists only caring about ``coffee cups" or ``doughnuts" caused me to name the ``Table of Contents" as ``Clay Mathematics" as you can see on the top of each and every single page, which is a quick link to go back, as well as the bottom right. Note: I was not aware of the Clay Mathematics Institution at all when I began to make this ``glossary", it was a happy coincidence.

So what do topologists actually do? Well...
\begin{center}
    Main goal of topology: Classify topological spaces up to \h.
\end{center}

But that is way too hard! So...

\begin{center}
    More realistic goal: Given topological spaces $X$ and $Y$, decide whether or not they are \hc.
\end{center}

Also note that: topologists are sometimes savages. So $\subset$ means ``subset" or ``inclusion" where as $	\subsetneq$ means ``proper subset" or ``proper inclusion". They also denote collection of set using script letter, like $\mathcal{P}\text{(The power set)}, \mathcal{B}\text{(The set of basis)}, \dots$

Anyway! So what's this ``glossary" actually about? Well, when I was busying getting my life totally destroyed by Topology, I found this way to be a really neat way for me to learn harder mathematical concept, and since I will go to graduate school for mathematics one day, it only makes sense for me keep on adding more and more to this document as well as the following:
\begin{enumerate}
    \item[1.] \href{https://www.overleaf.com/project/616b3a6756e3c97b342c6a36}{On-Going Analysis}
    \item[2.] \href{https://www.overleaf.com/project/61843474f70cad11d2caf20f}{Never-Ending Algebra}
\end{enumerate}

The creation of this document involves but not limited to 
\begin{enumerate}
    \item[1.] \emph{Topology} by James Munkers;
    \item[2.] \emph{Counterexamples in Topology} by Lynn Arthur Steen.
\end{enumerate}

And here's the most sincere thanks for all the support and encouragement I got when I was so beaten down by Topology and this Glossary wouldn't be made without you all: Dr. Matt Young, Jan-Luca, Jasper Swensen, Jessica Jorgensen, Hyrum Hansen, Dr. Micheal Shutlz, Dr. Justin Heavilin, and Dr. David Euler Brown.

\vfill

\begin{minipage}[b]{0.9\textwidth}
\footnotesize\raggedright
\setlength{\parskip}{0.5\baselineskip}
Copyright \copyright \, \the\year{} Xiang Gao\par
\end{minipage}
\vspace*{2\baselineskip}

{\protect\hypertarget{toc}{}}
\tableofcontents

\newpage 
\addcontentsline{toc}{part}{Part 1. Introduction to Topology}
\input{Math_5510/Math_5510.tex}

\newpage 
\addcontentsline{toc}{part}{Part 2. Counterexamples in Topology}
\input{Counterexamples_in_Topology/Counterexamples_in_Topology}

\newpage
\addcontentsline{toc}{part}{Appendices}
\input{Appendix_1/Appendix_1.tex}

\newpage
\input{Appendix_2/Appendix_2.tex}

\newpage
\input{Appendix_3/Appendix_3.tex}
\end{document}